Insert your title here

### 2018-08-12 sect3-exact-methods.tex
MI: the objective function in the decision version of the straightfwd model has been adjusted, becasue its original version did not give at most n-s, but in some instances gave something less than that. Now it is always n-s if the solution is feasible. The description has been updated accordingly.

%In Model \ref{mod:basic}, superscript of $x$-variables represents a time step in which a signal is transmitted along corresponding arc.
\subsubsection{Decision version}
\label{sec:decbasic}
The nature of MBT suggests another modelling approach derived from Model \ref{mod:basic}. 
For a given maximum broadcast time $t_{\text{max}}$, we maximize the number of arcs along which a signal is relayed within $t_{\text{max}}$.
If the optimal value is $n-1$, it is clear that we found a spanning broadcast tree with broadcast time $t_{\text{max}}$.
In case the optimal value is less than $n-1$, the gien $t_{\text{max}}$ is insufficient and we have to try solving the problem with increased time limit.
Clearly, an additional knowledge of upper and lower bound spares some computations. 
A lower bound is the initial value of $t_{\text{max}}$. 
Similarly, if an upper bound $\bar{t}$ is known and $t_{\text{max}}=\bar{t}-1$, the process can be terminated when the objective function is less then $n-1$, because $\bar{t}$ is than the optimal value.

The decision model \label{mod:basic:dec}  has the form
\begin{subequations}\label{mod:basic:dec}
\begin{align}
\label{mod:basic:dec:obj} \max \sum\limits_{(u,v) \in A}\sum\limits_{k=1}^{t_{\text{max}}}x_{u,v}^k \\ 
\notag \text{s. t. } \\
\label{mod:basic:dec:atMost1in} \sum\limits_{k=1}^{t_{\text{max}}}\sum\limits_{v\in N(u)}x_{vu}^k & \leq 1 & u\in V \setminus S,\\
\label{mod:basic:dec:0toSource} \sum\limits_{k=1}^{t_{\text{max}}}\sum\limits_{v\in N(u)}x_{vu}^k & = 0  & u\in S,\\
\notag \eqref{mod:basic:onefromroot}, \eqref{mod:basic:tIncreases}, \eqref{mod:basic:positiveCost},\\
\label{mod:basic:dec:dim}&&x \in \{0,1\}^{A\times V}.
\end{align}~
\end{subequations}

Constraint \eqref{mod:basic:singlein} is replaced by \eqref{mod:basic:dec:atMost1in} and \eqref{mod:basic:dec:0toSource}. 
The former is an inequality, because not all nodes are necessarily reached within the given time limit.
The latter makes sure that sources are not reached by any signal. 
This was filtered out by optimality in \eqref{mod:basic}, but it must be forbidden explicitly in \eqref{mod:basic:dec} due to the changed objective function.

The objective function \eqref{mod:basic:dec:obj} maximizes the number of arcs relaying a signal.
The actual target function is the minimum time required for spreading the signal to all nodes, and so we are looking for the smallest value of $t_{text{max}}$.
\subsection{Binomial tree model}

>>>>

%In Model \ref{mod:basic}, superscript of $x$-variables represents a time step in which a signal is transmitted along corresponding arc.
\subsubsection{Decision version}
\label{sec:decbasic}
The nature of MBT suggests another modelling approach derived from Model \ref{mod:basic}. 
For a given maximum broadcast time $t_{\text{max}}$, we maximize the number of nodes $v$ that receive a signal from some neighbor $u$ within $t_{\text{max}}$ time steps.
If the optimal value is $n-s$, it is clear that we found a spanning broadcast tree with broadcast time $t_{\text{max}}$.
In case the optimal value is less than $n-s$, the given $t_{\text{max}}$ is insufficient, and we have to try solving the problem with increased time limit.
Clearly, an additional knowledge of upper and lower bound spares some computations. 
A lower bound is the initial value of $t_{\text{max}}$. 
Similarly, if an upper bound $\bar{t}$ is known and $t_{\text{max}}=\bar{t}-1$, the process can be terminated even when the objective function is less then $n-s$, because $\bar{t}$ is than the optimal value.

The decision model \label{mod:basic:dec}  has the form
\begin{subequations}\label{mod:basic:dec}
\begin{align}
\label{mod:basic:dec:obj} \max \sum\limits_{v \in V\setminus S}\sum\limits_{u \in N(v)} \sum\limits_{k=1}^{t_{\text{max}}}x_{uv}^k \\ 
\notag \text{s. t. } \\
\label{mod:basic:dec:atMost1in} \sum\limits_{k=1}^{t_{\text{max}}}\sum\limits_{v\in N(u)}x_{vu}^k & \leq 1 & u\in V \setminus S,\\
\label{mod:basic:dec:0toSource} \sum\limits_{k=1}^{t_{\text{max}}}\sum\limits_{v\in N(u)}x_{vu}^k & = 0  & u\in S,\\
\notag \eqref{mod:basic:onefromroot}, \eqref{mod:basic:tIncreases}, \eqref{mod:basic:positiveCost},\\
\label{mod:basic:dec:dim}&&x \in \{0,1\}^{A\times V}.
\end{align}~
\end{subequations}

Constraint \eqref{mod:basic:singlein} is replaced by \eqref{mod:basic:dec:atMost1in} and \eqref{mod:basic:dec:0toSource}. 
The former is an inequality, because not all nodes are necessarily reached within the given time limit.
The latter makes sure that sources are not reached by any signal. 
This was filtered out by optimality in \eqref{mod:basic}, but it must be forbidden explicitly in \eqref{mod:basic:dec} due to the changed objective function.
The actual target function is the minimum time required for spreading the signal to all nodes, and so we are looking for the smallest value of $t_{\text{max}}$.
\subsection{Binomial tree model}
